Data Preparation

### 2019-01-18 Data Preparation.Rmd
minor changes to d_transcript

Our dataframe contains many variables and rows that are either empty or meaningless for our analysis. First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor"). Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
```{r}
d_transcript <- d_transcript %>%
  # only keep one observation (with the final grade) per student-course
  filter(`Appraisal (Description)` == "Grade supervisor", `Appraisal Type`=="7055") %>%
  select(`Student Number`,
         `Module (Abbrev.)`,
         `Module (Desc.)`,
         `Program (Abbreviation)`,
         `Grade symbol`,
         `Academic Year`,
         `Academic Session`,
         `Number rep. attemp`) %>%
  rename(`Student ID` = `Student Number`,
         `Course ID` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         Grade = `Grade symbol`,
         `Study Program` = `Program (Abbreviation)`,
         Year_numerical = `Academic Year`,
         Period = `Academic Session`,
         `Number Repeated Attempt` = `Number rep. attemp`) %>%
  distinct
```

>>>>

Our dataframe contains many variables and rows that are either empty or meaningless for our analysis. First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor"). Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
```{r}
d_transcript <- d_transcript %>%
  filter(`Appraisal (Description)` == "Grade supervisor", `Appraisal Type`=="7055") %>%
  select(`Student Number`,
         `Module (Abbrev.)`,
         `Module (Desc.)`,
         `Program (Abbreviation)`,
         `Grade symbol`,
         `Academic Year`,
         `Academic Session`,
         `Number rep. attemp`) %>%
  rename(`Student ID` = `Student Number`,
         `Course ID` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         Grade = `Grade symbol`,
         `Study Program` = `Program (Abbreviation)`,
         Year_numerical = `Academic Year`,
         Period = `Academic Session`,
         `Number Repeated Attempt` = `Number rep. attemp`) %>%
  distinct
```
